---
title: 'Exercise 5: Functions and Loops'
author: "Dillon Laaker"
date: "10/28/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
```

# Functions

1. Create a function for the mean, median, and standard deviation.
```{r}
national <- read.csv("national.csv")

mean <- function(x) { 
  return(mean(x))
}


median <- function(x) { 
  return(median(x))
}

sd <- function(x) { 
  return(sd(x))
}
```

2. Create a function that finds the mean and excludes the lowest and highest value.
```{r}
nat_mean_sub <- function(x){
  s <- sort(x) 
  sub <- s[-c(1, length(s))]
  return(sub)
}
```

3. Apply the functions to the Christianity variables.
```{r}
nat_mean_sub(national$christianity_all)
```

4. Write a function that lists all the unique years with more than 300,000 Christians in total.
```{r}
fun_3k <- function(d,x,y){ #make a new function d will be data, x is my parameter, y is the year
  f <- as.data.frame(d[x>300000, y]) #f is what i call the first dataframe in my data my row has to be greater than 300000 and then I select for year
  u <- unique(f) #not i need to sleect for unique values of my year
  return(u) #return 
}

C_300 <- fun_3k(national, national$christianity_all, 'year')
head(C_300)
```
# Loops/apply

1. Write a loop to find how many variables there are per observation.
```{r}
nrow(national)
mat <- data.frame(matrix(ncol = 1, nrow = nrow(national)))
for (i in 1:nrow(national)){ mat[i,1] <- ncol(national)}
head(mat)
```
2. Write a loop to find the mean number of Protestant Christians in each country (i.e., the state column). Then use an apply family function to do the same.
```{r}
l <- unique(national$state)
m <- data.frame(matrix(ncol = 2, nrow = nrow(data.frame(l))))

for(i in 1: length(l)){
  x<- national |> filter(state == l[i]) |>
    summarise(m_PC = mean(christianity_protestant)) |>
    pull(m_PC)
  m[i, 1] <- l[i]
  m[i, 2] <- x
}
```
3. Check the column type for each variable.
```{r}
m2 <- tapply(national$christianity_protestant, national$state, mean)
sapply(national,class)
```


