---
title: "Graphics"
author: "Marika Olijar"
date: "11/19/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
```

Create the following graphs in `ggplot2`.

1. Check out the base R built-in dataset, `data("USArrests")`.
```{r}
data("USArrests")
```
2. Create a scatterplot that looks at the correlation between murder and assault arrests. Label the x and y axes and title the graph.
```{r}
ggplot(USArrests) + 
  aes(x = Murder, y = Assault) +
   labs(title = "Aussault vs. Murder Arrests in the US") +
  geom_point(colour = "skyblue2")
```

3. Create a boxplot of rape arrests. Label the plot.
```{r}
ggplot(USArrests) +
  labs(title = "1973 Rape Arrests in the US") +
  aes(Rape,) +
  geom_boxplot(fill = "skyblue2", colour = "blue")
```

4. Create a barplot of the number of rape arrests per state.
```{r}
state.names = row.names(USArrests)
ggplot(USArrests) +
  aes(Rape, state.names) +
  labs(title = "1973 Rape Arrests in US States") +
  geom_bar(stat='identity', fill = "skyblue2", colour = "blue")
```

5. Create a histogram for the percent of urban population.
```{r}
state.names = row.names(USArrests)
ggplot(USArrests) +
  aes(UrbanPop) +
  labs(title = "1973 % Urban Population") +
  geom_histogram(fill = "skyblue2", colour = "blue")
```